\chapter{Introduction}
\label{ch:introduction}

This report summarizes the work accomplished during my two-and-a-half-year post-doctoral position
 at the Institute of High Energy Physics (IHEP), Beijing, from October 2022 to December 2024.
 My primary focus has been on various physics analyses and contributions to software and
 hardware development tasks within the CMS collaboration at CERN.

\section*{Overview of Physics Analyses}

During this tenure, I have been involved in the following key physics analyses:
\begin{itemize}
    \item \textbf{Resonant Di-Higgs search in the \HHWW channel:} \\
    A search for resonant Higgs boson pair production, analyzing the di-Higgs process using the
    \HHWW decay mode.
    We studied both the semi-leptonic and fully hadronic final states of W-bosons.
    This analysis targets all event topologies, including highly boosted, semi-boosted,
    and fully resolved configurations, as well as cases where leptons are reconstructed inside jets,
    improving the sensitivity across the mass range of interest.

    \item \textbf{High mass scalar searches:} \\
    Model-independent searches for high-mass scalar resonances in the \XZZ and \XZZv channels,
    exploring the mass range up to 3 TeV.
    These studies provide significant constraints on possible beyond-the-Standard-Model (BSM) scenarios.

    \item \textbf{Differential and fiducial cross-section measurement in the \HToFourL channel:} \\
    A precision measurement of the Higgs boson production cross-sections, utilizing the clean \HToFourL
    decay channel, which provides an excellent test of the Standard Model (SM) predictions.

    \item \textbf{Anomalous Triple Gauge Coupling (aTGC) studies using the \WpWm channel:} \\
    Analyzing $WW$ production to probe anomalous triple gauge couplings,
    which are critical to understanding potential deviations from the SM predictions.

    \item \textbf{Higgs boson mass measurement in the \HGG channel:} \\
    A precise determination of the Higgs boson mass using the \HGG decay mode,
    exploiting its clean signature in the CMS electromagnetic calorimeter.

    \item \textbf{VH production studies:} \\
    Analyzing the associated production of the Higgs boson with vector bosons ($VH$),
    which plays an essential role in understanding the Higgs coupling to $W$ and $Z$ bosons.

    \item \textbf{High-Granularity Calorimeter (HGCAL) studies:} \\
    Contributions to the R\&D and performance evaluation of the HGCAL,
    which is a critical upgrade for the CMS detector in preparation for the High-Luminosity LHC (HL-LHC) phase.

    \item \textbf{Effective Field Theory (EFT) studies:} \\
    Exploring potential deviations from the SM using EFT parameterizations,
    particularly in Higgs boson and di-boson production processes.
\end{itemize}

\section*{Technical Contributions and Detector Operations}

In addition to the above physics analyses, I contributed to several technical tasks essential for the CMS experiment:
\begin{itemize}
    \item \textbf{High-Level Trigger (HLT) development for electrons and photons:} \\
    Optimization and development of HLT algorithms for electron and photon identification,
    improving event selection efficiency for CMS physics analyses.

    \item \textbf{Monte Carlo sample generation with MadGraph:} \\
    Production of simulated event samples using MadGraph, which are crucial for the validation of physics
    analyses and background estimation.

    \item \textbf{Detector Control System (DCS) shifts:} \\
    Performed Detector Control System (DCS) shifts at P5 (CMS experimental site),
    ensuring smooth operation and monitoring of detector subsystems.

    \item \textbf{HGCAL cleanroom shifts:} \\
    Participated in several shifts at the HGCAL cleanroom, contributing to module testing and
    quality assurance processes.
\end{itemize}

\section*{Structure of the Report}

The remainder of this report is organized as follows:
\begin{itemize}
    \item \textbf{Chapter~\ref{ch:diHiggsSearcehs}:} Details on the resonant di-Higgs search in the \HHWW channel, including analysis strategy and results.
    \item \textbf{Chapter~\ref{ch:highMassSearches}:} Results of the high-mass scalar searches in the \XZZ and \XZZv channels.
    \item \textbf{Chapter~\ref{ch:differentialFiducialXS_H4l}:} Description of the differential and fiducial cross-section measurement in the \HToFourL
    channel.
    \item \textbf{Chapter~\ref{ch:aTGC}:} Analysis and results of the anomalous triple gauge coupling studies in the \WpWm channel.
    \item \textbf{Chapter~\ref{ch:massMeasurement}:} Higgs boson mass measurement in the \HGG channel.
    \item \textbf{Chapter~\ref{ch:egamma}:} Technical contributions, including HLT developments and Monte Carlo sample generation.
    \item \textbf{Chapter~\ref{ch:conclusion}:} Summary and outlook for future studies.
\end{itemize}

This comprehensive report reflects my contributions to both the physics analysis program and
the technical advancements within the CMS collaboration at IHEP.
